Library Parser

### 2024-06-07 studies/library_parser.qmd
add working regression example to library parser

**Status** in progress.

@@

>>>>

**Status:** in progress.

**TODO**: - Separate scripts and functions into separate .qmd files/directories. - Update `model_rate_emotion_values` nomenclature process for classification papers.

@@

```{r}
classification_studies = subset(meta_df_unpacked, paradigm == " classification  ")

sapply(1:nrow(classification_studies), function(i) {
  print(i) 
  print(eval(parse(text = classification_studies$model_rate_emotion_values[i])))
}
)
```

```{r eval = F}
regression_studies = subset(meta_df_unpacked, paradigm == " regression  ")

sapply(1:nrow(regression_studies), function(i) {
  print(i) 
  print(eval(parse(text = regression_studies$model_rate_emotion_values[i])))
}
)
```

```{r}
# low-level function to extract relevant values from named array
model_result_2_df <- function(x) {
  # get algorithm name from variable at beginning of string (before parsing)
  toolbox <- trimws(stringr::str_extract(x, pattern = "[^\\=]+"))
  print(toolbox)
  # now evaluate the expression
  x <- rlang::eval_tidy(rlang::parse_expr(x))
  # get name of fitted models from column names
  model_names <- colnames(x)
  # print(model_names)
  # split across model name for summary statistic (e.g., mean, sd, etc.)
  model_statistic <- str_split(model_names, '\\.')
  model_statistic <- unlist(lapply(model_statistic, function(x) x[2]))
  # get values
  model_values <- as.numeric(x)
  # names(model_values) <- 'score'
  print(model_values)
  # get additional attributes (feature.data.exp)
  model_attributes <- rownames(x)
  print(model_attributes)
  data.frame(model_attributes)
  # get additional model details
  model_attributes <- str_split_1(model_attributes, '\\.')
  names(model_attributes) <- c('feature_id', 'data_id', 'experiment_id')
  # split across '_' to 
  model_measures <- data.frame(do.call('rbind', str_split(colnames(x), '_')))
  print(model_measures)
  names(model_measures) <- c('dimension', 'measure')
  model_measures_split <- str_split(model_measures[,'measure'], '\\.')
  model_measures[,'measure'] <- unlist(lapply(model_measures_split, 
                                              function(x) x[1]))
  return(data.frame(toolbox, 
             t(model_attributes), 
             model_measures, 
             values = model_values,
             statistic = model_statistic))
}

# high level function to apply model_result_2_df to multiple studies
get_study_summaries <- function(df) {
  do.call(rbind,
          lapply(df$model_rate_emotion_values, 
                 FUN = function(x) {
                   study_id <- unique(df$citekey[which(df$model_rate_emotion_values == x)])
                   model_results <- model_result_2_df(x)
                   return(cbind(study_id, model_results))
                   }
                 )
          )
}

# Parsing Regression Studies

The following functions provide a working example for converting the r code contained in `model_rate_emotion_values` to a data frame for further analysis (currently working for regression studies).

### Template

Encoded values should use the following nomenclature:

```         
library = rbind(features.data.exp = c(dim_measure.summary = 0.5, dim_measure.summary = 0.1), features.data.exp = c(dim_measure.summary = 0.2, dim_measure.summary = 0.5))

# e.g.

librosa = rbind(mfcc.msd.1 = c(valence_r2.mean = 0.5, arousal_r2.mean = 0.1), 
temporal.msd.1 = c(valence_r2.mean = 0.2, arousal_r2.mean = 0.5,
valence_r2.sd = 0.1, arousal_r2.sd = 0.1))
```

### Working example

```{r}
this_study <- data.frame(citekey = c('testStudy2023ab','testStudy2023ab', 'testStudy2020of'),
  model_rate_emotion_values = c("marsyas = rbind(mfcc.msd.1 = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5,
                                  valence_r2.sd = 0.4, arousal_r2.sd = 0.3,
  valence_mse.mean = 0.3, arousal_mse.mean = 9.1))",
  "librosa = rbind(mfcc.ismir.1 = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3,
                                  valence_r2.sd = 0.2, arousal_r2.sd = 0.4,
  euclid_euclid.mean = 0.32, euclid_euclid.sd = 0.1))",
  "mirtoolbox = rbind(pitch.filmMusic.2 = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3))")
)
```

### Summary data frame

```{r}
knitr::kable(get_study_summaries(this_study))
```
